Competence distance

### 2017-03-03 analysis/analysis_competence.Rmd
update

# Read data 
```{r, echo=FALSE}
machine <- 'ajpelu'
# machine <- 'ajpeluLap'
di <- paste('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

@@

```{r}
focal_trees <- unique(compete$id_core)

@@

df_indices_plot <- bind_rows(output)
```

```{r}
# Some constante variables 
radius_plot <- 10 # radius plot (10 m)
sf_plot <- pi * radius_plot^2 # surface plot (m2)

den_tree <- compete %>% 
  filter(sp != 'Focal') %>% 
  group_by(id_core) %>% 
  summarise(ntree = n(), 
            stand_density = ntree*10000 / sf_plot ) # stand density (tree / ha)

diameter = perimeter/pi

ba <- compete %>% 
  mutate(dn = (diam_mm/1000) / pi, 
         dn2 = dn * dn) %>% 
  group_by(id_core) %>% 
  summarise(
    ba = (pi/4) * sum(dn2),
    ba_mean = ba / n())

get_coords_trees <- function(angle, distance, x0, y0) {
  angle <- ifelse(angle <= 90, 90 - angle, 450 - angle)
  data.frame(x = x0 + distance * cos(angle / 180 * pi),
             y = y0+ distance * sin(angle / 180 * pi))
}

compete <- compete %>% 
  mutate(xcord = get_coords_trees(angle= rumbo_degree, 
                           distance = distance_cm/100,
                           x0 = 0, y0 = 0)$x,

         ycord = get_coords_trees(angle = rumbo_degree, 
                           distance = distance_cm/100,
                           x0 = 0, y0 = 0)$y)

@@

compete %>%  
  ggplot(aes(x=xcord, y=ycord)) + 
  facet_wrap(~id_core) + 
  geom_point(aes(size=diam_mm), shape=21, fill='transparent') + 
  xlim(-11,11) + ylim(-11,11) + 
  geom_point(aes(x=0, y=0), color='green') +
  theme_bw() +
  gg_circle(radius = 10, xcenter = 0, ycenter = 0) +
  theme(panel.grid.major=element_blank(), 
        panel.grid.minor=element_blank())

radi <- 10 
(pi*radi*radi)/10000

den <- compete %>% group_by(id_core) %>% 
  summarise(ntree = n(),
            den = ntree*10000 / (pi*100))

# Extract data
```{r} 
ditemp <- paste('/Users/', machine, '/Documents/', sep='')
setwd(ditemp)

# read DEM 
demsn <- raster("mde_sn_area_influencia.asc")

setwd(di)

## Projection 
# Get projection
projection(demsn)

# Set projection
crs(demsn) <- "+proj=utm +zone=30 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"

# Read points data 
gps_point <- readOGR(paste0(di, 'data_raw/geoinfo/'), layer = 'dendro_garmin', verbose = FALSE)

## reproject 
gps_point_re <- spTransform(gps_point, crs(demsn))

gps_elev <- extract(demsn, gps_point_re, method='simple', sp=TRUE)

elev <- gps_elev@data %>% 
  dplyr::select(lat, lon, elev, name, date, elev_mde = mde_sn_area_influencia)

# Export data
write.csv(elev, file=paste(di, "/data/elev.csv", sep=""), row.names = FALSE)
```

>>>>

# Read data 
```{r, echo=FALSE}
#machine <- 'ajpelu'
machine <- 'ajpeluLap'
di <- paste('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

@@

## Compute competence index

`TODO` documentar

```{r}
focal_trees <- compete %>% filter(id_core != 'Fresno') 
focal_trees <- unique(focal_trees$id_core)

@@

df_indices_plot <- bind_rows(output)

rm(n_competitors, n_competitors_hihger, plot_density, stand_density, sum_sizes, size_ratio, dist_nn, df, df_indices, output, df_more_indices, dnft)
```

## Plot

```{r}
get_coords_trees <- function(angle, distance, x0, y0) {
  angle <- ifelse(angle <= 90, 90 - angle, 450 - angle)
  data.frame(x = x0 + distance * cos(angle / 180 * pi),
             y = y0+ distance * sin(angle / 180 * pi))
}

compete <- compete %>% 
  mutate(xcord = get_coords_trees(angle= rumbo_degree, 
                           distance = distance_cm/100,
                           x0 = 0, y0 = 0)$x,
         ycord = get_coords_trees(angle = rumbo_degree, 
                           distance = distance_cm/100,
                           x0 = 0, y0 = 0)$y)
```

compete %>%  
  filter(sp != 'Focal') %>%
  ggplot(aes(x=xcord, y=ycord)) + 
  facet_wrap(~id_core) + 
  geom_point(aes(size=perim_mm), shape=21, fill='transparent') + 
  xlim(-11,11) + ylim(-11,11) + 
  geom_point(aes(x=0, y=0), color='green') +
  theme_bw() +
  gg_circle(radius = 10, xcenter = 0, ycenter = 0) +
  theme(panel.grid.major=element_blank(), 
        panel.grid.minor=element_blank()) 
```

@@
